State and Parameter Estimation for Spatio-Temporal Neural Fields

### 2010-05-01 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
changes to paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    INSTITUTE OF PHYSICS PUBLISHING                                   %
%                                                                      %
%   `Preparing an article for publication in an Institute of Physics   %
%    Publishing journal using LaTeX'                                   %
%                                                                      %
%    LaTeX source code `ioplau2e.tex' used to generate `author         %
%    guidelines', the documentation explaining and demonstrating use   %
%    of the Institute of Physics Publishing LaTeX preprint files       %
%    `iopart.cls, iopart12.clo and iopart10.clo'.                      %
%                                                                      %
%    `ioplau2e.tex' itself uses LaTeX with `iopart.cls'                %
%                                                                      %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
% First we have a character check
%
% ! exclamation mark    " double quote  
% # hash                ` opening quote (grave)
% & ampersand           ' closing quote (acute)
% $ dollar              % percent       
% ( open parenthesis    ) close paren.  
% - hyphen              = equals sign
% | vertical bar        ~ tilde         
% @ at sign             _ underscore
% { open curly brace    } close curly   
% [ open square         ] close square bracket
% + plus sign           ; semi-colon    
% * asterisk            : colon
% < open angle bracket  > close angle   
% , comma               . full stop
% ? question mark       / forward slash 
% \ backslash           ^ circumflex
%
% ABCDEFGHIJKLMNOPQRSTUVWXYZ 
% abcdefghijklmnopqrstuvwxyz 
% 1234567890
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% \documentclass[twocolumn,11pt,a4paper]{article}		%<-use this for checking equation length
\documentclass[12pt]{iopart}

%<-comment out this for checking equations (author list too)
\usepackage{iopams,setstack} 
%<-comment out this for checking equations
\usepackage{graphicx}
\usepackage{algorithm, algorithmicx, algpseudocode} 
\usepackage{color} 
\usepackage[tight,scriptsize]{subfigure}
% \usepackage{pstool}
\renewcommand{\subcapsize}{\small}
% \usepackage{anysize}							%<-use this for checking equation length
% \marginsize{1.7cm}{1.5cm}{0.3cm}{0.8cm}			%<-use this for checking equation length
% \setlength{\columnsep}{0.5cm}					%<-use this for checking equation length
\usepackage{amssymb,amsfonts} 			%<-use this for checking equation length
\newcommand{\todo}[1]{\textsf{\emph{\textbf{\textcolor{blue}{#1}}}}} 
\newcommand{\wtf}[1]{\textsf{\emph{\textbf{\textcolor{red}{#1}}}}} 
\newcommand{\omg}[1]{\textsf{\emph{\textbf{\textcolor{green}{#1}}}}} \begin{document}

@@

\author{Dean R. Freestone$^1$, Parham Aram$^2$, Michael Dewar$^3$, Kenneth Scerri$^4$, David B. Grayden$^1$, and Visakan Kadirkamanathan$^2$}

\address{$^1$ Department of Electrical and Electronic Engineering, University of Melbourne, Melbourne, Vic, 3010 Australia} \address{$^2$ Department of Automatic Control and Systems Engineering, University of Sheffield, Mappin Street, Sheffield, S1 3JD, UK} \address{$^3$ Department of Applied Physics and Applied Mathematics, Columbia University, US} \address{$^4$ Ken's} \ead{dfreestone@bionicear.org} 
\begin{abstract}
	Will do the abstract towards the end. 
\end{abstract}

@@

The sensors were spaced in a regular square grid, where the number of sensors was 100, sensor width $\sigma^2_m$ was 1.44 which equals $2$~mm full width at half maximum, with spacing $\Delta_y$ equal to $2.22$~mm. This arrangement modelled the recording as having some cross talk, which is typical from neurophysiological recordings. Note, sensor design to guarantee representation of the field can be achieved using the frequency analysis from section~\ref{SpectralAnalysisSection} given access to the true field. \omg{From frequency analysis the separation is $2.77$, with $\rho = 2$ (note same as basis function).} 
\begin{figure}\label{fig:experimental design}
	\begin{center}
		\includegraphics[scale=0.6]{./Graph/ExperimentFigure.pdf} 
	\end{center}
	\caption{Example of experimental design and model output. \textbf{A}. Example of the neural field with sensors. The centres of the sensors are shown by crossed and the sensor widths ($1/2$ height of Gaussian) are shown by the circles. \textbf{B} Example of data generated by the model through the observations. \textbf{C}. Power spectral density of the data generated by an observation showing the typical $1/f$ characteristic of iEEG.} \label{fig:FrequencyAnalysis} 
\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    INSTITUTE OF PHYSICS PUBLISHING                                   %
%                                                                      %
%   `Preparing an article for publication in an Institute of Physics   %
%    Publishing journal using LaTeX'                                   %
%                                                                      %
%    LaTeX source code `ioplau2e.tex' used to generate `author         %
%    guidelines', the documentation explaining and demonstrating use   %
%    of the Institute of Physics Publishing LaTeX preprint files       %
%    `iopart.cls, iopart12.clo and iopart10.clo'.                      %
%                                                                      %
%    `ioplau2e.tex' itself uses LaTeX with `iopart.cls'                %
%                                                                      %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
% First we have a character check
%
% ! exclamation mark    " double quote  
% # hash                ` opening quote (grave)
% & ampersand           ' closing quote (acute)
% $ dollar              % percent       
% ( open parenthesis    ) close paren.  
% - hyphen              = equals sign
% | vertical bar        ~ tilde         
% @ at sign             _ underscore
% { open curly brace    } close curly   
% [ open square         ] close square bracket
% + plus sign           ; semi-colon    
% * asterisk            : colon
% < open angle bracket  > close angle   
% , comma               . full stop
% ? question mark       / forward slash 
% \ backslash           ^ circumflex
%
% ABCDEFGHIJKLMNOPQRSTUVWXYZ 
% abcdefghijklmnopqrstuvwxyz 
% 1234567890
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\documentclass[twocolumn,11pt,a4paper]{article}		%<-use this for checking equation length
% \documentclass[12pt]{iopart}

%<-comment out this for checking equations (author list too)
% \usepackage{iopams,setstack} 
%<-comment out this for checking equations
\usepackage{graphicx}
\usepackage{algorithm, algorithmicx, algpseudocode} 
\usepackage{color} 
\usepackage[tight,scriptsize]{subfigure}
% \usepackage{pstool}
\renewcommand{\subcapsize}{\small}
% \usepackage{anysize}							%<-use this for checking equation length
% \marginsize{1.7cm}{1.5cm}{0.3cm}{0.8cm}			%<-use this for checking equation length
% \setlength{\columnsep}{0.5cm}					%<-use this for checking equation length
\usepackage{amsmath}
\usepackage{amssymb,amsfonts} 			%<-use this for checking equation length
\newcommand{\todo}[1]{\textsf{\emph{\textbf{\textcolor{blue}{#1}}}}} 
\newcommand{\wtf}[1]{\textsf{\emph{\textbf{\textcolor{red}{#1}}}}} 
\newcommand{\omg}[1]{\textsf{\emph{\textbf{\textcolor{green}{#1}}}}} \begin{document}

@@

% \author{Dean R. Freestone$^1$, Parham Aram$^2$, Michael Dewar$^3$, Kenneth Scerri$^4$, David B. Grayden$^1$, and Visakan Kadirkamanathan$^2$}
% 
% \address{$^1$ Department of Electrical and Electronic Engineering, University of Melbourne, Melbourne, Vic, 3010 Australia} \address{$^2$ Department of Automatic Control and Systems Engineering, University of Sheffield, Mappin Street, Sheffield, S1 3JD, UK} \address{$^3$ Department of Applied Physics and Applied Mathematics, Columbia University, US} \address{$^4$ Ken's} \ead{dfreestone@bionicear.org} 
\begin{abstract}
	Will do the abstract towards the end. 
\end{abstract}

@@

The sensors were spaced in a regular square grid, where the number of sensors was 100, sensor width $\sigma^2_m$ was 1.44 which equals $2$~mm full width at half maximum, with spacing $\Delta_y$ equal to $2.22$~mm. This arrangement modelled the recording as having some cross talk, which is typical from neurophysiological recordings. Note, sensor design to guarantee representation of the field can be achieved using the frequency analysis from section~\ref{SpectralAnalysisSection} given access to the true field. \omg{From frequency analysis the separation is $2.77$, with $\rho = 2$ (note same as basis function).} 
% \begin{figure}\label{fig:experimental design}
% 	\begin{center}
% 		\includegraphics[scale=0.6]{./Graph/ExperimentFigure.pdf} 
% 	\end{center}
% 	\caption{Example of experimental design and model output. \textbf{A}. Example of the neural field with sensors. The centres of the sensors are shown by crossed and the sensor widths ($1/2$ height of Gaussian) are shown by the circles. \textbf{B} Example of data generated by the model through the observations. \textbf{C}. Power spectral density of the data generated by an observation showing the typical $1/f$ characteristic of iEEG.} \label{fig:FrequencyAnalysis} 
% \end{figure}
\begin{figure}[!hb] 
% \renewcommand*{\thesubfigure}{}
\centering
\subfigure[][]{\includegraphics[width=3in]{./Graph/ExperimentFigurePy.pdf}}\\
% \hspace{2.5mm}
\subfigure[][]{\includegraphics[width=3in]{./Graph/ExperimentFigureEEGPy.pdf}}\\
% \hspace{2.5mm}
\subfigure[][]{\includegraphics[width=3in]{./Graph/ExperimentFigurePSDPy.pdf}}
\caption{Example of experimental design and model output. \textbf{A}. Example of the neural field with sensors. The centres of the sensors are shown by crossed and the sensor widths ($1/2$ height of Gaussian) are shown by the circles. \textbf{B} Example of data generated by the model through the observations. \textbf{C}. Power spectral density of the data generated by an observation showing the typical $1/f$ characteristic of iEEG.} \label{fig:FrequencyAnalysis} 
\end{figure}
